\cvsection{Experience}
\begin{cventries}
  \cventry
    {Co-Founder \& Chief Technology Officer}
    {WingWork, Inc.}
    {Seattle, WA}
    {March 2023 - Present}
    {
      \begin{cvitems}
        \item {Spearheaded Wingwork's founding, securing \$4.5M funding; acquired 3 enterprise customers in first 6 months, growing to 20+ total.}
        \item {Launched MVP in 4 months; validated product-market fit across multiple aviation segments with 90\%+ client retention.}
        \item {Drove technical demos and customer success initiatives resulting in early renewals and strong referrals.}
        \item {Engineered AI document search saving mechanics 5-8 hours weekly (250-400 hours annually) across client operations.}
        \item {Built founding engineering team fostering rapid iteration, scalable architecture, and customer-led development.}
        \item {Architected maintenance tracking, document hub, and multi-tenant RAG-based AI assistant for compliance.}
        \item {\textbf{Technologies}: TypeScript, React, GraphQL, PostgreSQL, AWS, Prisma, Cloudflare, Supabase, RedwoodJS (legacy)}
      \end{cvitems}
    }
    {}
    {}
  \cventry
    {Senior Software Engineer}
    {Meta Platforms (Facebook)}
    {Menlo Park, CA}
    {April 2020 - March 2023}
    {
      \begin{cvitems}
        \item {Reduced advertiser support costs by 60\% through innovative AdsManager tools, boosting retention rates.}
        \item {Unified codebase across 17+ products, enhancing cross-product functionality.}
        \item {Led team transition during company-wide reorganization with zero productivity loss.}
        \item {Built data platform reducing metric time-to-market by 75\%, improving UX and privacy controls.}
        \item {Led privacy initiative across 80+ teams ensuring regulatory compliance and data protection.}
        \item {Mentored 40+ new hires, accelerating onboarding and fostering knowledge sharing.}
        \item {\textbf{Technologies}: Hack, React, GraphQL, Presto}
      \end{cvitems}
    }
    {}
    {}
  \cventry
    {Senior Software Engineer}
    {Rubrik, Inc.}
    {Palo Alto, CA}
    {Jan 2018 - April 2020}
    {
      \begin{cvitems}
        \item {Built automated code validation workflow reducing build breakages by 90\%.}
        \item {Reduced code validation latency by 75\% through remote execution implementation.}
        \item {Orchestrated migration of 20+ build/test workloads to cloud, creating robust disaster recovery across multiple services.}
        \item {Engineered custom Jenkins plugin enhancing developer experience with seamless test verification pipeline integration.}
        \item {\textbf{Technologies}: Python, Jenkins, AWS, MSSql, Django, Celery}
      \end{cvitems}
    }
    {}
    {}
  \cventry
    {Software Design Engineer}
    {Imagination Technologies}
    {Santa Clara, CA}
    {July 2015 - Jan 2018}
    {
      \begin{cvitems}
        \item {Developed web-based control center for FPGA emulation platform management, serving 10+ cross-functional teams.}
        \item {Implemented continuous validation framework for MIPS CPU testing, enabling more frequent releases.}                
        \item {Implemented and maintained CI/CD pipelines using Buildbot/Jenkins for FPGA builds.}
        \item {Boosted platform utilization by 75\% and doubled throughput through process optimization.}
        \item {\textbf{Technologies}: Python, JavaScript, Python-Flask, Buildbot, Jenkins}
      \end{cvitems}
    }
    {}
    {}
  % \cventry
  %   {Software Engineer Intern}
  %   {DreamWorks Animation}
  %   {Glendale, CA}
  %   {Sept. 2014 - Apr. 2015}
  %   {
  %     \begin{cvitems}
  %       \item {Built components for continuous integration/deployment in automation and testing.}
  %       \item {Developed tools enhancing the reliability of the animation validator suite.}
  %       \item {\textbf{Technologies}: C++, Python, and Cassandra(CRUD)}
  %     \end{cvitems}
  %   }
  %   {}
  %   {}
  % \cventry
  %   {Software Development Engineer Intern}
  %   {Amazon Inc}
  %   {Seattle, WA}
  %   {May 2014 - Aug. 2014}
  %   {
  %     \begin{cvitems}
  %       \item {Implemented a product scoping feature to sort item variations on Amazon.}
  %       \item {Created a web-based servicing tool for clients.}
  %       \item {This tool cut down trouble tickets by 70-80\%.}
  %       \item {\textbf{Technologies}: Java, JavaScript, Spring MVC, DynamoDB and Amazon Internal tools}
  %     \end{cvitems} 
  %   }
  %   {}
  %   {}
\end{cventries}